Figures and results for main manuscript

### 2021-05-08 analysis/reports/submission2/manuscript_main_rev.Rmd
I think I want to revert fig 6, idk

ggsave("figure_2.pdf", plot = fig_2, device = "pdf", width = 180, height = 180, dpi = 800, units = "mm")
# 
signif(as.numeric(example_di$nparts), digits = 2)[1]
(as.numeric(example_di2$nparts))[1]
as.numeric(example_di3$nparts)[1]

@@

```{r f6, fig.dim = c(6,8)}

all_di <- all_di %>%
  mutate( `Number of elements` = ifelse(nparts < 2000, "Less than 2000", "More than 2000"))
diss_results <- all_di %>%
  filter(nparts > 20) %>%
  group_by(Dataset,  `Number of elements` ) %>%
  summarize(high_diss = mean(real_po_percentile_excl > 95),
            nsites = dplyr::n()) %>%
  ungroup() %>%
  mutate(`High dissimilarity` = paste0(signif(100 * high_diss, 2), "%; n = ", nsites)) %>%
  select(-nsites)

@@

nhist <- plot_narrowness_hist(filter(all_di, dat %in% c("fia", "mcdb", "misc_abund")), "skew_95_ratio_2t", "Skewness") +
  facet_wrap(vars(`Number of elements`, Dataset), scales = "free_y", nrow = 2, ncol = 3) +
  xlab("Breadth index") +
  ylab("Number of communities") +
  ggtitle("Skewness") + theme(plot.margin = unit(c(5,5,5,5), units = "mm"))

phist <- plot_percentile_hist(filter(all_di, dat %in% c("fia", "mcdb", "misc_abund")), "skew_percentile_mean", "Skewness") +
  facet_wrap(vars(`Number of elements`, Dataset), scales = "free_y", nrow = 2, ncol = 3) +
  xlab("Percentile rank of observed value relative to feasible set") +
  ylab("Number of communities") +
  ggtitle("Skewness")+ theme(plot.margin = unit(c(5,5,5,5), units = "mm"))

@@

ggsave("figure_6.pdf", plot = fig_6, device = "pdf", width = 180, height = 180, dpi = 800, units = "mm")

>>>>

ggsave("figure_2.pdf", plot = fig_2, device = "pdf", width = 180, height = 120, dpi = 800, units = "mm")
# 
signif(as.numeric(example_di$nparts), digits = 2)[1]
(as.numeric(example_di2$nparts))[1]
as.numeric(example_di3$nparts)[1]

@@

```{r f6, fig.dim = c(6,8)}
plot_percentile_hist_small <- function(di_df, col_name, plot_name, tails = 2, facetvar = "Dataset", min_s0 = 0) {

  ggplot(filter(di_df, nparts > min_nparts, s0 >= min_s0), aes(response)) +
    geom_histogram(bins = 40, boundary = 100) +
    theme_bw() +
    xlab("") +
    ylab("") +
    geom_vline(xintercept = cutoff_percentiles, color = "red") +
    ggtitle( plot_name) +
    #geom_text(data = distinct(select(di_df, Dataset)), aes(x = 45, y = 100, label = Dataset)) +
    facet_wrap(vars(facetvar), ncol = 1, scales = "free_y")+
    theme(plot.title = element_text(size=9), axis.text = element_text(size = 6), strip.text = element_text(size = 7), strip.placement = "inside") +
    scale_y_continuous(n.breaks = 3)

}
all_di <- all_di %>%
  mutate( `Number of elements` = ifelse(nparts < 2000, "Less than 2000", "More than 2000"))
diss_results <- all_di %>%
  filter(nparts > 20) %>%
  group_by(Dataset,  `Number of elements` ) %>%
  summarize(high_diss = mean(real_po_percentile_excl > 95),
            nsites = dplyr::n()) %>%
  ungroup() %>%
  mutate(`High dissimilarity` = paste0(signif(100 * high_diss, 2), "%; n = ", nsites)) %>%
  select(-nsites)

@@

nhist <- plot_narrowness_hist(filter(all_di, dat %in% c("fia", "mcdb")), "skew_95_ratio_2t", "Skewness") +
  facet_wrap(vars(`Number of elements`, Dataset_short), scales = "free_y", nrow = 2, ncol = 2) +
  xlab("Breadth index") +
  ylab("Number of communities") +
  ggtitle("Skewness") + theme(plot.margin = unit(c(0,5,0,2), units = "mm"), axis.text = element_text(size = 6) ,strip.text = element_text(size = 7), strip.placement = "inside")

phist <- plot_percentile_hist_small(filter(all_di, dat %in% c("fia", "mcdb")), "skew_percentile_mean", "Skewness")  +
  facet_wrap(vars(`Number of elements`, Dataset_short), scales = "free_y", nrow = 2, ncol = 2) +
  xlab("Percentile rank of observed value \nrelative to feasible set") +
  ylab("Number of communities") +
  ggtitle("Skewness")+ theme(plot.margin = unit(c(0,5,5,2), units = "mm"), plot.title = element_text(size = 10))

@@

ggsave("figure_6.pdf", plot = fig_6, device = "pdf", width = 80, height = 150, dpi = 800, units = "mm")
